---
title: "Predict particular activity base on accelerometers"
author: "Anna"
date: "2016年8月21日"
output: html_document
---


## Overview

Normally, people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. This report will research it, use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. 

## Prepare data

```{r,  results='hide', include=FALSE, warning=FALSE}
library(lattice)
library(ggplot2)
library(caret)
library(randomForest)
library(lars)
library(gbm)


setwd("~/programming/learning/DataScience/assignment/Practical_Machine_Learning/lesson4")

```

Read data form local files.

```{r , echo=TRUE}
testing <- read.csv("./data/pml-testing.csv")
training <- read.csv("./data/pml-training.csv")
dim(testing)
dim(training)
```

## Clean data

Remove the all NAs column in test and train data.

```{r , echo=TRUE}
isTestNAsCol <- sapply(testing, function (x) any(is.na(x) | toString(x) == ""))
testNames <- names(isTestNAsCol)[!isTestNAsCol]
# pick up  belt, forearm, arm, and dumbell 
testNames <-  testNames[grepl("belt|arm|dumbbell|forearm", testNames)]
trainNames <- c("classe", testNames)
```

Subset traing data to include testNames, and check the validity of the data

```{r , echo=TRUE, results='hide'}
trainClean <-  training[, trainNames]
isTrainNAsCol <- sapply(trainClean, function (x) any(is.na(x) | toString(x) == ""))
# the two length is 52, trainClean data is valid
length(names(trainClean)[!isTrainNAsCol]) # 52
length(names(trainClean)) # 52
testClean <- testing[, testNames]
dim(trainClean) #19622*52
dim(testClean)  #20*52
```


## Split data

```{r, echo=TRUE}
set.seed(123)
#create training set indexes with 70% of data
inTrain <-createDataPartition(trainClean$classe, p=0.70, list=F)
trainData <- trainClean[inTrain, ]
testData <- trainClean[-inTrain, ]
```


## Modeling

```{r, echo=TRUE, cache=TRUE}
fitRf <- train(classe ~ ., data=trainData, method="rf", 
                   trControl=trainControl(method = "cv",5), ntree=200)
```


Now, Obtain the accuracy on the test data.

```{r, echo=TRUE}
predictRf <- predict(fitRf, testData)
confusionRes <- confusionMatrix(testData$classe, predictRf)
accuracy <- confusionRes$overall[1]
accuracy
```

Frome above result, the model's accuracy is 99.29%, and error ratio is less than %1.

## Predict on the test data

```{r, echo=TRUE}
predictTest <- predict(fitRf, testClean)
predictTest
```
